The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-11-15 donde.tex
limited and balanced attrition - analysis for internal validity

In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 20\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 20\%.  Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment on the Treated.  We find modest selection on gains but nonetheless significant positive benefits of commitment even for those who would not have chosen it.  %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.

@@

@@

\paragraph{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at anytime with no penalty for pre-payment. No reminders or interim contact exists between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece \textit{and} any payments made. Before the contract expired, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and same piece as the original one a (26\% of borrowers renew at least once with a given pawn). This contract was standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.  When asked why they are pawning this piece, 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).

\paragraph{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (43\%), recovered their pawn (44\%), or whether they are censored in our data (13\%). The first thing to note is that those that default incur in higher costs; part of this is mechanical as losing their collateral is part of the cost. The second thing to note is that those that are not closed at the end of our sample period have already incurred in substantial financial cost, even though they have not defaulted yet. Panel (b) shows the APR; most of the APR costs come from clients that do not recover their pawn. 
%Of those who renew, 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn. Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}

@@

\vspace{.2in}
\noindent \textbf{Randomization.}  Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$. The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes. In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size. %Thus we eliminated {the smallest} ones. 
Branches are more than 5 km apart from each other, and there is little substitution among them; only 1\% of consumers appear in more than one of our branches.

@@

\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.

\paragraph{Survey data.} In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before treatment status was known to them. The survey was intentionally short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 10,437 clients, and the survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.

@@

\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.  Narrative reports and the way the treatment was implemented make us believe that selection into treatment is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.} If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.  To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day. The first row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=0.06), but we cannot reject equality with the Forced Commitment arm (p-value=0.41), or across all arms (p-value=0.16).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.  In no arm did more than three percent of individuals who responded to the survey go on to refuse loans, and neither these rates nor the rate of survey response are different across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

>>>>

In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 22\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%.  Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment on the Treated.  We find modest selection on gains but nonetheless significant positive benefits of commitment even for those who would not have chosen it.  %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.

@@

The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.  While most of the academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.  \cite{Laibson2018} has referred to this implicit bundling of commitment devices as ‘private paternalism’, and its logic is that individuals may benefit from commitment and yet not explicitly demand it.  Comparing voluntary versus paternalistic programs requires that we form counterfactuals for two different groups of people: those who would naturally choose commitment, and those who would not (since the latter group is treated only under paternalist policies). In this paper we present an experimental design and analysis structure that \textcolor{teal}{point-identifies} and provides estimates for both, the treatment on the treated (TOT), as well as the treatment on the untreated (TUT). This permits a clear window into the case for paternalistic (forced) rather than voluntary commitment in financial services.

%The relationship between treatment effects and willingness to accept treatment is a core concern in the econometrics literature. 
\textcolor{teal}{The literature has estimated the TOT and the TUT under a variety of techniques.}
By relaxing the often restrictive parametric assumptions of classic sample selection models, the Marginal Treatment Effects (MTE) approach \citep{heckman2007econometric} provides a powerful toolbox for studying this relationship. In principle, MTE methods allow researchers to use observational data and a single excluded instrument to compare treatment effects across those who are willing and unwilling to accept treatment. In practice, however, unless the instrument has an extremely rich support set, this difference of treatment effects can only be point identified by using additional modeling assumptions to extrapolate beyond the information contained in the data \citep{mogstad2018using}. \textcolor{teal}{Another research strategy uses} Becker-Degroot-Marschak (BDM) mechanisms, incentivizing choice prior to treatment assignment to elicit willingness to pay (WTP) for treatment \citep{becker1964measuring}. %If subjects have standard preferences, then the BDM mechanism is incentive-compatible and the elicited distribution of WTP does not depend on the distribution from which prices were drawn. 
A number of studies, however, find that the elicited WTP changes arbitrarily with the distribution of prices used in the elicitation exercises \citep{bohm1997eliciting,banerji2014detection} %, casting considerable doubt on the assumption of standard preferences.
\textcolor{teal}{making elicitation unreliable, and suggesting subjects have non-standard preferences, in which case BDM would lose the incentive-compatibility property} %In general, the BDM mechanism is no longer incentive compatible if subjects have non standard preferences 
\citep{mamadehussene2023reliability}. %For this reason, WTP elicited via the BDM mechanism may not provide a good proxy for real-world treatment take-up. 
This study overcomes the two difficulties above by combining a novel three-armed randomized experiment (control, forced treatment, and treatment choice arms) with two mild and transparent exclusion restrictions, to point identify the relevant TOT and TUT in a real-world, high-stakes setting. This allows us to study the case for paternalistic commitment head-on, with minimal assumptions.

We implement the study in an important and understudied context: that of pawnshop lending. We run an experiment covering close to 5,000 pawnshop clients in 6 branches of a lender in Mexico City. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default and so lose their pawn as well as any payments made towards principal.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} In this context we implement a ``commitment choice'' arm, in which borrowers can voluntarily opt into a structured repayment contract at the time of taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if that payment is delinquent. This fee serves as a reminder and a means of reinforcing the importance of these interim payments. In addition, we include a ``forced commitment'' arm, in which all borrowers are \emph{required} to repay using the structured monthly contract, the one offered on an opt-in basis in the commitment choice arm.

The combination of voluntary and forced commitment within the RCT allows us to address several key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely we are able to ask whether the \textit{right} borrowers voluntarily demand commitment. This ability comes from our unique three-armed experimental design, which we call the ``controlled choice design'' for short.  We go beyond the average treatment effect (ATE). Our design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance; one of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose (TOT),
while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT).

%Our design point identifies not only the overall effect of forced commitment---the average treatment effect (ATE)---but also the effect of commitment for borrowers who would \emph{voluntarily} choose it (TOT) along with the effect of commitment for borrowers who would \emph{not} (TUT).  
By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$. This enables us to test --not assume-- whether borrowers who voluntarily choose commitment have higher average treatment effects than those who do not. The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes. Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more complete and economically-relevant picture of the effects of commitment. We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.

This controlled choice design is key to measuring the effects of mandated versus voluntary imposition of product features, \textcolor{teal}{and thus a first step in understanding what \cite{Laibson2018} calls `private paternalism'.  This question is of interest in a large class of cases. Financial contracts for instance already have a high dose of private paternalism and forcing features: most contracts have built-in frequent payments for instance. But beyond finance, in education, most teachers mandate homework with deadlines to deal with procrastination \citep{Ariely}. In the workplace, firms monitor employee attendance,\footnote{\url{https://www.wsj.com/lifestyle/careers/attention-office-resisters-the-boss-is-counting-badge-swipes-5fa37ff7}.} but also set and monitor time-specific goals. In the public policy domain we have seatbelt mandates, age-dependent medical checkups, etc., which often go beyond nudging. Having a rigorous way to estimate the causal effects of mandates vs choice policies ---and not just for the average individual--- is critically important.}

%categorized by \cite{Laibson2018} as possessing `private paternalism’ where commitment is involuntarily embedded into product features (classroom requirements and exams in schools, employee monitoring in the workplace, or highly structured financial contracts).  
The question of whether people choose what is right for themselves is particularly salient in pawn lending, \textcolor{teal}{as these pawn borrowers often need to borrow for emergencies under significant stress\footnote{There is a large literature showing that stress impairs cognitive function, e.g. \cite{StressReview}.}. They are also more likely to have little schooling, financial education, and formal credit market access.}  The Pawn loans industry is interesting in itself. It is one  of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. For example, there are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in Mexico in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).}

One last highlight. Interestingly, pawnshop lending presents an inverted lending case: since these loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.  Our partner's standard pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that can be paid back anytime before the loan comes due at no penalty. This contract, which may cause default, is the standard contract in the industry. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature. Thus, while our paper makes a methodological point, the substantive results in the application are important for this understudied industry, and could be applied more broadly whenever mandates vs choice is under consideration.  %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments.   To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner that is not obvious to borrowers. Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.

Coming to our results. We find that commitment is strongly effective in preventing default in pawnshop lending, with the average individual in the forced arm paying financing costs inclusive of fees that are 22\% lower than the control, while default decreases by 6.6 percentage points (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 11 percentage points (19\% of the mean). That is, by imposing the structure of commitment it is possible to save borrowers money by charging them fees! These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using each borrower's subjective value of the pawn rather than the appraised value of the gold, and adjusting for lost liquidity from requiring monthly payments.

The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not.  By inducing borrowers either to fully recover, or to default without making any payments, the monthly payment contract saves money that would otherwise have been paid towards loans that ultimately default, money which is lost to the borrower.  In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit is 7.9 percentage points higher. Commitment contracts also decrease by 7 percentage points the fraction of borrowers who make a payment but ultimately fail to recover their pawn.  Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the commitment contract induces people who would otherwise pay something towards recovery but default to instead pay more and faster, making them more likely to recover their pawn at a lower financial cost. We find this bifurcation mechanism interesting and little discussed in the literature.

In spite of a large average treatment effect documenting financial cost savings, only 11\% of borrowers in the choice arm actually choose commitment. If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. Can the borrowers who did not choose commitment be those who simply don’t need it? We address this question by sequentially imposing more structure on the problem. 
%We find that borrowers who are assigned the forced commitment contract are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract. One potential interpretation of this result is that borrowers who experience the frequent payment contract rationally choose to borrow more later on because of the lower effective financial costs that this contract entails.\footnote{An alternative interpretation is that the monthly payments from the commitment contract sap borrowers liquidity, leading them to take a second loan to pay off the first. This is unlikely because subsequent loans fall outside the 90 day period within which payments for the first loan are due. Moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments. We test this and we cannot reject that demand is higher after experiencing the monthly payment contract, however sample sizes are small and power for this analysis is correspondingly low.

We start our analysis of heterogeneity by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distributions in the treatment and control arms as in \cite{fan2010sharp}. We find that at least 23\% of individual borrowers benefit from commitment, implying many borrowers did not demand it even though their individual treatment effect is positive. Next, we impose the exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to that contract.\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TUT. We then estimate that the financial cost savings of the TUT is large, at \$192 pesos, equivalent to 10.6 percentage point savings in APR. That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.%\footnote{We estimate a positive TOT that is larger than the TUT, but it is imprecise--this results from the smaller sample size, given that few chose the monthly payment contract--and the hypothesis of TOT=TUT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}

What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?  While a simple measure of time inconsistency does not predict heterogeneity in our study, we show substantial levels of over-optimism among borrowers. Among borrowers who do not choose it, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan. The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

In a final step, we impose a selection-on-observables assumption and use the Causal Random Forest algorithm of \cite{atheygrf} to estimate conditional average treatment effects (both ATEs and TUTs) for the individual borrowers in our experiment.  We estimate that 93\% of the borrowers who did not opt for the commitment contract have positive conditional TUT effects, while only 37\% of those who chose commitment have negative conditional TOT effects.   While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even the random forest only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).

Our paper makes a number of contributions to the literature.   Two other recent papers also shed some light on private paternalism. In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment, suggesting a lack of awareness as to self-control problems. In the context of school choice, \cite{Walters} finds that students who select into more effective schools have smaller treatment effects from attending than those who do not. Our paper differs from these in both its empirical setting and its methodology. As far as we are aware, ours is the first experiment to combine control, forced treatment, and treatment choice arms and explain how such a design can be used to point identify TUT effects and a range of other interesting causal parameters under minimal assumptions. While \cite{fowlie2021default} likewise exploited a three-armed experimental design in their study of the effect of electricity pricing, they identified two TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.

Other approaches to going beyond local average treatment effects (LATE) from the literature either assume no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate} (the ``LATE-and-reweight'' approach) or rely on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits} (the marginal treatment effects approach).  \cite{Walters} takes the latter approach, combining a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates that differ substantially from those implied by a LATE-and-reweight approach. In contrast, we leverage our experimental design to point identify the TUT effect using a binary instrument without the need for a structural model, relying instead on relatively weak exclusion restrictions. This restriction has testable implications that we fail to reject. Rather than assuming away unobserved selection-on-gains, as in the LATE-and-reweight approach, we estimate it directly. Unlike \cite{Sprenger} we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.  In a returns-to-education setting, \cite{oreopoulos2006estimating}, uses a similar direct approach to identify a LATE \emph{nearly} equals a TUT effect: the 1944 Butler Act increased the share of British children who remained in school until age 15 from 43\% to over 90\%. Because 100\% of borrowers in our forced arm are treated, we identify the TUT rather than an approximation to it.

Our study also speaks to recent research on the effects of payment frequency. While experiments in microfinance markets have not shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure. These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our results. Second, we provide a deeper analysis of both the take-up and efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}) while others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). Unlike all of these papers, however, we separately point identify and estimate the effects of commitment for borrowers who would and would not choose it. This allows us to conduct a more rigorous and nuanced analysis of private paternalism in our empirical context.

Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context. 
The remainder of the paper is structured as follows:  Section \ref{context} provides context and defines our main outcome variables. Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms. Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} presents our strategy for estimating ToT and TuT effects, and Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted.  Section \ref{conclusion} concludes.

\begin{comment}
%OLD INTRODUCTION:

@@

\paragraph{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at anytime with no penalty for pre-payment. No reminders or interim contact exists between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece \textit{and} any payments made. Before the contract expired, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and same piece as the original one (38\% of borrowers renew at least once with a given pawn). This contract was standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a `non-urgent expense'.  When asked why they are pawning this piece, 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (72\%).

\paragraph{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). The first thing to note is that those that default incur in higher costs; part of this is mechanical as losing their collateral is part of the cost. The second thing to note is that those that are not closed at the end of our sample period have already incurred in substantial financial cost, even though they have not defaulted yet. Panel (b) shows the APR; most of the APR costs come from clients that do not recover their pawn. 
%Of those who renew, 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn. Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}

@@

\vspace{.2in}
\noindent \textbf{Randomization.}  Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$. The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes. In four of them the experiment ran for 102 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size. %Thus we eliminated {the smallest} ones. 
Branches are more than 5 km apart from each other, and there is no substitution among them; none of the consumers appear in more than one of our branches.

@@

\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 8,519 pawns, and our administrative data cover a total of 26,180 pawns.

\paragraph{Survey data.} In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before treatment status was known to them. The survey was intentionally short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 7,210 clients, and the survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.

@@

\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.  Narrative reports and the way the treatment was implemented make us believe that selection into treatment is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.}

If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms. That is, if potential borrowers disliked being forced into a commitment contract so much so as to leave the branch, we would expect a lower number of pawns on branch days where only the commitment contract is available. Table \ref{attrition_table} shows that this is not the case. There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day. Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms\footnote{p-value=0.23 and 0.12 respectively.}. This seems to be due to sampling variance. The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece). Figure \ref{boxplot_attrition} shows that entire distributions across arms overlay pretty well with one another, with the choice arm having a few more outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns is numerically the same across arms.}
